Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2012-01-10 article.tex
Some of Nick's comments
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1458 ccdd05d5-56c1-461a-bf98-85f6876523b4

Perhaps another way to deal with line features with coherence times much longer than the templates would be to entrirely `factor' the whitening out of the \lloid\ filter bank.  Any line features could be notched out in the whitening stage with IIR filters, which can achieve infinitely high $Q$ at just second order.  If the detector data were passed through the whitening filter twice, then time-sliced filters need not depend on the detector's noise power spectral density at all.  In such a variation on the \lloid\ method, the basis filters could be calculated from the \emph{weighted} \SVD~\citep[chapter 3.6]{WeightedSVD, jackson2003user} of the time-sliced templates, using the covariance of the detector noise as a weight matrix.

>>>>

Another way to deal with line features with coherence times much longer than the templates would be to entirely `factor' the whitening out of the \lloid\ filter bank.  Any line features could be notched out in the whitening stage with IIR filters, which can achieve infinitely high $Q$ at just second order.  If the detector data were passed through the whitening filter twice, then time-sliced filters need not depend on the detector's noise power spectral density at all.  In such a variation on the \lloid\ method, the basis filters could be calculated from the \emph{weighted} \SVD~\citep[chapter 3.6]{WeightedSVD, jackson2003user} of the time-sliced templates, using the covariance of the detector noise as a weight matrix.
